\documentclass[12pt,a4paper,oneside]{article}
\usepackage[a4paper]{geometry}
\setlength\parindent{0pt}

\begin{document}

\begin{itemize}
  \item Name: Pinglei Guo
  \item Assignment: Write-Ahead log
  \item Last Modified: \today
\end{itemize}

1. What is the problem authors are trying to solve

\medskip

Crash recovery, the durability in ACID. Committed transaction must be written to disk, on going transactions
aborted due to system crash must be rolled back.

\bigskip

2. How does the authors’ approach or solution improve on previous approaches to that problem

\medskip

ARIES's algorithm is relatively simple compared with other WAL, like it redo all the transaction and then undo
those "loser", while other systems redo "non-loser". Also compared with shaow page method, log is more light weight
thus improve database throughput and reduce disk usage.

\bigskip

3. Why is this work important

\medskip

Because it's useful for both durability and concurrency control (consistency).
Database is an abstraction of data, all the clients have the illusion that they
have exclusive access to the data, just like all the process have the illusion that
they have exclusive access to CPU (by time slicing) and Memory (by virtual memory).
And this can also be applied to filesystem, maybe OS as well? Seems most system
softwares have log/journal for recovery.

\bigskip

4. Your comments/questions

\medskip

Questions

\begin{itemize}
  \item In order to guarantee the durability of the log, it is written to several disks,
what if the crash result in different disk have different copies.
  \item What happens to indexes when recovery?
  \item Is it possible to dumping the whole database snapshot, like I have
2GB data in RAM and I dump a 2GB file in the disk, so when I recovery, I just load the whole
dump, and use some copy on write tricks to allow transactions when I am dumping. It should
be faster than appling log, cause I have the final state in the dump, while log is actually
replaying everything that has happended, and sometimes it's a wast.
i.e. transaction A inserted 100 entries and transaction B deleted those 100 entries,
the final state has nothing to do with those 100 entries,
but when using WAL, I have to do these in fact useless work.
Maybe I can analysis the log and omit those useless work?
  \item If the data is immutable, i.e. what is inserted will never be updated, like for time series,
sensor data of temperature can't have another value once it is recorded. The database itself would
be like a log, except it need to have better read spead than sequencial files. WAL might be useless.
  \item Buffer manager is mentioned in the paper, which acts pretty like virtual memory,
and we know \textit{mmap} can map file into memory, I've watched a course from Andrew Pavlo
and he says no serious database use \textit{mmap}. I am wondering since current memory is so
big compared to the old time, maybe it's ok to let system handle all the page in page out, since
it would be pretty rare to page out when you have 64GB of RAM and 2GB of data.
  \item The Log should be pretty large, and ARIES did mentioned archive, is it possible to
compress the logs when archive, like use some specific algorithm that knows the structure of
the log instead of general ones like GZIP, LZMA.
  \item ARIES also mentioned tape when it comes to archive and I heard Google is also using tape for long term backup,
I was wondering what tape really is, cause my idea of tape is the music tape that I put in my walkman back in primary school.
Is the tape technology back at ARIES time same as the tape Google and Amazon using nowadays.
  \item Where are all those guys writing database in IBM now? It seems only government and
tranditional companies are still using things from IBM (at least this is the case in China).
\end{itemize}

Miscellaneous

\begin{itemize}
  \item ARIES is actually the name of the algorithm, I was thinking it's the name of the database
like System R
  \item IBM had so many on going database project at that time, that's pretty different from my
impression of IBM China, where most people are just waiting for retirement
  \item In the Database Managment Systems book, the crash recovery chapter use ARIES as example,
and there is a footnote I like most, "Nothing is guaranteed in life except death and taxes"
\end{itemize}

\end{document}
