\documentclass[12pt,a4paper,oneside]{article}
\usepackage[a4paper]{geometry}
\setlength\parindent{0pt}
\usepackage{hyperref}

\begin{document}

\begin{itemize}
  \item Name: Pinglei Guo
  \item Assignment: Relational Cloud: A Database as a Service for the Cloud
  \item Last Modified: \today
\end{itemize}

1. What is the problem authors are trying to solve

\medskip

Build a multi tenacy database as service to decrease the cost per user.

\bigskip

2. How does the authors’ approach or solution improve on previous approaches to that problem

\medskip

\begin{itemize}
  \item Integerate with CryptDB to imporve privacy, DB Admin can't snoop most data.
\end{itemize}

\bigskip

3. Why is this work important

\medskip

Because maintain database has huge cost and cloud is the trend.

\bigskip

4. Your comments/questions

\medskip

Questions

\begin{itemize}
	\item A lot problem it mentioned are solved now. VM is replaced by container (i.e. docker), lightweight virtualization
  reduce the overhead of virtualization. Resource monitoring and scheduling can be solved with frameworks like Mesos and Kubernetes.
  , with consideration of stateful services like Database.
  And for obtaining the pattern of the workload, there are databases using machine learning to get the pattern.
  \item From the paper I can't see how their design is better than AWS and Azure except the CryptDB part.
  \item The development seems stop after 2013, the url only has a wiki with some notes on it.
\end{itemize}

\end{document}
