\documentclass[12pt,a4paper,oneside]{article}
\usepackage[a4paper]{geometry}
\setlength\parindent{0pt}
\usepackage{hyperref}

\begin{document}

\begin{itemize}
  \item Name: Pinglei Guo
  \item Assignment: Write-Behind Logging
  \item Last Modified: \today
\end{itemize}

1. What is the problem authors are trying to solve

\medskip

Using NVM with DRAM (not NMV alone) to improve the performance of database in
durability and recovery.

\bigskip

2. How does the authors’ approach or solution improve on previous approaches to that problem

\medskip

\begin{itemize}
  \item Use Write-Behind Logging to make use of the fast speed of NVM and random access (compared to block access with SSD)
  \item Remove the redo and undo phase in ARIES
  \item Support both two tier (DRAM, NVM) and three tier (DRAM, NVM, SSD/HDD), while previous apporaches are single tier (NVM only)
\end{itemize}

\bigskip

3. Why is this work important

\medskip

It utilize NVM to avoid the overhead of writing values in log, which can allow SSD to run longer
and support more data in database with same disk space.
NVM is still very immature (they used an emulator \url{http://pmem.io/}), but it might be the future of storage.

\bigskip

4. Your comments/questions

\medskip

Questions

\begin{itemize}
  \item There are TPC-C, TPC-H, TPC-*, why they only choose TPC-C, and as I know,
Peloton is designed to be a hybrid OLTP \& OLAP database (Pavlo mentioned ), while YCSB is used to benchmark
systems that does not fit into TPC-* well, like DyanmoDB (large k-v), HBase. As
an hybrid database, YCSB does not fit into both OLTP \& OLAP.
  \item The detail for replication is not provided (or I missed it), they said extra
construct is needed because WBL does not have value like WAL. And since it involve on fly
compute, is it possible the CPU usage would become a bottle neck?
  \item Only primary secondary replication is considered, and what about chain replication
and other more advacned replications, for more than one host, it may involve some consistent
algorithm like Paxos and Raft.
  \item The size of the main memory is not well discussed, what if the main meory is same or
even larger than NVM, like it's normal to see 64GB memory in normal user's home, not to mention
server-class machines.
\end{itemize}

Miscellaneous

\begin{itemize}
  \item Pavlo published a paper about a benchmark framework called OLTP-Bench \url{https://github.com/oltpbenchmark/oltpbench}
But he didn't mention it in this paper
  \item This paper discussed MVCC with WAL, which is what previous course mentioned but didn't have time to cover
\end{itemize}

\end{document}
